### 2018-11-25 chapters/1-introduction.tex
the

Various different fitting methods have been applied for modeling PCa DWI signal
decay. The biexponential function \citep{Mulkern2006} provides the best fitting
quality for DWI data sets acquired using ``high'' b values ($\sim$2000 s/mm²)
\citep{Jambor2015Evaluation}. The biexponential function is not robust to
noise and has low repeatability. In contrast, kurtosis function
\citep{Jensen2005} provides similar fitting quality while being substantially
more robust to noise \citep{Jambor2015Evaluation}. However, texture
features of parametric maps derived from the kurtosis function have not been
evaluated and hold promise by better signal characterization compared with the
most commonly used monoexponential function \citep{Toivonen2015}. Other MRI
methods, such as T₂-mapping (T₂) and anatomical T₂-weighted imaging (T₂w), could
provide complimentary information to DWI for prediction of PCa characteristics
\citep{Jambor2015Relaxation}.

@@

The aim of this study was to use carefully optimized high quality MRI data sets
to develop and validate machine learning methods for non-invasive Gleason score
prediction, meaning prediction of PCa aggressiveness. In this study, we built
and evaluated a classifier system based on multiple texture features of high
quality T₂w, DWI (monoexponential and kurtosis functions), and T₂ relaxation
maps for prediction of PCa Gleason score dichotomized as 3+3 (low risk) vs >3+3
(high risk). Moreover, we explored which combinations of imaging modalities and
texture extraction methods are most useful for Gleason score prediction.

>>>>

Various different fitting methods have been applied for modeling PCa DWI signal
decay. The biexponential function \citep{Mulkern2006} provides the best fitting
quality for DWI data sets acquired using ``high'' b values ($\sim$2000 s/mm²)
\citep{Jambor2015Evaluation}. The biexponential function is not robust to
noise and has low repeatability. In contrast, the kurtosis function
\citep{Jensen2005} provides similar fitting quality while being substantially
more robust to noise \citep{Jambor2015Evaluation}. However, texture
features of parametric maps derived from the kurtosis function have not been
evaluated and hold promise by better signal characterization compared with the
most commonly used monoexponential function \citep{Toivonen2015}. Other MRI
methods, such as T₂-mapping (T₂) and anatomical T₂-weighted imaging (T₂w), could
provide complimentary information to DWI for prediction of PCa characteristics
\citep{Jambor2015Relaxation}.

@@

The aim of this study was to use carefully optimized high quality MRI data sets
to develop and validate machine learning methods for non-invasive Gleason score
prediction, meaning prediction of PCa aggressiveness. In this study, we built
and evaluated a classifier system based on multiple texture features of high
quality T₂w, DWI (the monoexponential and kurtosis functions), and T₂ relaxation
maps for prediction of PCa Gleason score dichotomized as 3+3 (low risk) vs >3+3
(high risk). Moreover, we explored which combinations of imaging modalities and
texture extraction methods are most useful for Gleason score prediction.
